N-Body problem

### 2014-10-25 article/article.tex
Adds future work

\section{Future work}

>>>>

\section{Future work}
For future work we would like to recommend to try a time-step scale for each body, meaning that close encounters have smaller time-step scale than other bodies. This should lead to a smaller energy error while not slowing down the whole process. Also, many calculations are suitable for parallelization to speed up the computing process.
